---
title: "Getting Started with the Shiny EDA Explorer"
author: "Ted Laderas"
date: "5/15/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What you need before you get started

If you are on your own laptop, make sure that the following packages are installed.

```{r eval=FALSE}
library(shiny)
library(tidyverse)
library(data.table)
```

You can install them with the following statement:

```{r eval=FALSE}
install.packages("shiny", "tidyverse", "data.table")
```

## Signing into the RStudio Instance 

We've created an account for you on our RStudio instance. To get there, open your browser to:

http://church.ohsu.edu:8787/

And log in with your info.

## Grab the GitHub Repo

Go to http://github.com/laderast/cvdNight1/ and download the repo as a zip file (it's the green button).

Now we'll upload the zip file to the server. On the *Files* tab in the lower right of your RStudio window, click "Upload", and upload the zip file to the server.

## Now open the project

In your folder that was created on the server, there is a file called `cvdWorkshop.Rproj`. Click on it to initialize the project.

## Start Running the App

You're almost there! Open the `global.R` file. If you are on your laptop, you can use the 
`runApp` button. 

If you're on our RStudio instance, the runApp button is broken. Instead, you will need to input the following commands.

```{r eval=FALSE}
library(shiny)
runApp()
```